---
title: "Sicegar Figures      Samples: SCV038, SCV039, SCV040, SCV041"
author: "Mehmet Umut Caglar"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 120)
```


```{r initials, include=FALSE}
###*****************************
# INITIAL COMMANDS TO RESET THE SYSTEM
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(14159)
###*****************************


###*****************************
# Set Working Directory
# One needs to arrange the correct pathway if this is not umut's computer ;)
if(as.vector(Sys.info()["effective_user"]=="umut"))
{
  setwd(paste0("/Users/umut/GitHub/Guo_etal_SCV/finalResultsRMarkDown/"))
} # mac computer
###*****************************


###*****************************
#Load Libraries
require(ggplot2)
require(cowplot)
require(reshape2)
require(tidyr)
require(dplyr)

require(grid)
require(gridExtra)
require(lazyeval)
require(pwr)
require(xtable)
require(htmlTable)
###*****************************


###*****************************
# Source functions
source("sicegarTableFunction.R")
source("replaceFunction.R")
source("singleVariableHistogramFunction.R")
source("doubleVariablePlottingFunction.R")
source("saveFigureDataFunction.R")
###*****************************
```



```{r cache=FALSE, echo=FALSE}
# read all the code chunks
knitr::read_chunk('sicegar_chunks.R')
```


Here is the association table of sample names and conditions, colored with respect to condition color used in figures.

```{r parameters, echo=FALSE, warning=FALSE}
###*****************************
# Color codes & conditions of the experiment sets used
# Test Name & Data Load & Colors
testName="15Aug2017"
listFileNames=c("SCV038","SCV039","SCV040","SCV041") # <- simply change this to pick up correct data
listConditionNames=c("WT_50", "WT_5000", "HR_50", "HR_5000") # <-  They are associated labels for datasets
listOrderNames=c("WT_50", "WT_5000", "HR_50", "HR_5000") # <- They are the order of labels 

colVec01=c("#e41a1c", "#377eb8", "#4daf4a","#984ea3") # <- simply change this to change figure colors
###*****************************
htmlTable(as.matrix(data.frame("File names"=listFileNames,"Conditions"=listConditionNames)),
           col.rgroup = colVec01)
```


```{r Generate data sets that will be used for plots, include=FALSE}
```





## The Aim of Distriburion Analysis

This part of document includes figures representing the distribution of labels associated with samples. Can give idea about percentage distributions of classes (like: "no signal", "infection", "infection&lysis") and distribution of problematic samples (like: "dirt", "dried out", "multiple infections")


```{r Generate data sets that will be used for plots, include=FALSE}
```


### Distibutions

```{r Distribution of labels, echo=FALSE, include=FALSE}
```




Here once more the figures side by side

```{r Distribution of labels WIDE, echo=FALSE, warning=FALSE, fig.width=22, fig.height=7}
```


### Distribution of DDOM

```{r Distribution of DDOM data, include=FALSE}
# calculates necessary DF
```

```{r Distribution of DDOM, echo=FALSE, warning=FALSE, fig.width=12.5, fig.height=7}
```



## The Aim of Single Variable Analysis

This part of document includes single variable figures associated with samples. We focus on 5 parameters: maximum, shape, midpoint, infection time, start point. For all parameters we investigate either the entire set of infections (i.e both "infection" and "infection & lysis"), or we only investigate the "infection & lysis" cases. 

For each figure we include tables showing p-values from t.test, Mann-Whitney U Test (wilcox.test), ,ean differences between conditions and the effect size. The tables also show the sample size for each condition.



### Maximum

```{r Maximum Associated figures and tables, echo=FALSE, warning=FALSE, fig.show="hide"}
```




Here are the figures side by side

```{r Maximum Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```



Following is the violin graph representing the distribution of maximums

```{r Maximum Associated violin, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```






### Slope

```{r Slope Associated figures and tables, echo=FALSE, warning=FALSE, fig.show="hide"}
```




Here are the figures side by side

```{r Slope Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```


Following is the violin graph representing the distribution of slopes

```{r Slope Associated violin, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```










### Midpoint

```{r Midpoint Associated figures and tables, echo=FALSE, warning=FALSE, fig.show="hide"}
```


Here are the figures side by side

```{r Midpoint Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```




Following is the violin graph representing the distribution of midpoints

```{r Midpoint Associated violin, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```







### Infection Time

```{r Infection time Associated figures and tables, echo=FALSE, warning=FALSE, fig.show="hide"}
```


Here are the figures side by side

```{r Infection time Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```

Following is the violin graph representing the distribution of infection time

```{r Infection time associated violin, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```





### Start point

```{r Start point Associated figures and tables, echo=FALSE, warning=FALSE, fig.show="hide"}
```



Here are the figures side by side

```{r start point Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```

Following is the violin graph representing the distribution of start point

```{r Start point associated violin, echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}
```


## The Aim

This document includes double variable figures associated with samples. For all parameters we investigate either the entire set of infections (i.e both "infection" and "infection & lysis"), or we only investigate the "infection & lysis" cases. For each graph we plot density and point versions. 

The investigated parameter couples are

1.) Midpoint vs Slope
2.) Slope vs Maximum
3.) Midpoint vs Maximum


### Midpoint vs Slope

```{r Midpoint vs Slope Associated figures and tables, include=FALSE}
```



```{r Midpoint vs Slope Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=15}
```



### Slope vs Maximum

```{r Slope vs Maximum Associated figures and tables, include=FALSE}
```



```{r Slope vs Maximum Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=15}
```










### Midpoint vs Maximum

```{r Midpoint vs Maximum Associated figures and tables, include=FALSE}
```


```{r Midpoint vs Maximum Associated figures and tables WIDE, echo=FALSE, warning=FALSE, fig.width=14, fig.height=15}
```

